\newcommand{\experienceItemListStart}{\begin{itemize}}
\newcommand{\experienceItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\experienceDeatils}[5]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} \textbar\hspace{0.2em}\text{#2} & \text{#3} \\ 
        \textbf{Tech Stack:} \text{#4} & \text{#5}\\
    \end{tabular*}
}
\newcommand{\experienceDeatilsWithCert}[6]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} \textbar\hspace{0.2em}\href{#6}{#2} & \text{#3} \\ 
        \textbf{Tech Stack:} \text{#4} & \text{#5}\\
    \end{tabular*}
}

%=================================
% 
%=================================
\vspace{-5pt}
\section{\large \textbf{WORK EXPERIENCE}}
    \resumeSubHeadingListStart
        \experienceDeatils
        {Highspot}
        {Software Development Engineer}
        {08/2025 – Present}
        {React.js, GraphQL, TypeScript, Ruby, MongoDB}
        {Hyderabad}
        \vspace{-5pt}
         \experienceItemListStart
            \ProjectItem{Created 25+ tiles, charts, and tables with drilldowns, using React, GraphQL and Ruby for team analytics scorecard.} 
            \ProjectItem{Implemented Blueprint-Based Visualizations to generate charts from reports, covering 90\% existing bar charts.}
            \ProjectItem{Built end-to-end RolePlay Scorecard from scaffold to dataviews, featuring advanced CRM filter integration.}
            \ProjectItem{Migrated 2 legacy scorecards to a new blueprint-based scorecard with charts and an enhanced People filter.}
        \experienceItemListEnd
       \vspace{4.5pt}
        \experienceDeatilsWithCert
        {Zscaler, Inc}
        {Software Development Engineer Intern}
        {02/2025 – 08/2025}
        {Java Spring Boot, Python, Bash/Shell Scripting, OpenTelemetry, Pytest, CI/CD}
        {Bangalore}
        {https://www.credly.com/badges/6d8db15a-4bec-4729-855e-6faf7650847c}
        \vspace{-5pt}
         \experienceItemListStart
            \ProjectItem{Architected a complete pytest automation framework integrated with GitLab CI/CD, covering 50+ test cases.} 
            \ProjectItem{Developed a sampling mechanism using Java Spring Boot, OTELv0.128.0 to efficiently collect and monitor performance.}
            \ProjectItem{Implemented PII masking for sensitive data in system logs, enhancing data processing security.}
            \ProjectItem{Achieved 91\% data compression by evaluating 5 compression algorithms and implementing the most efficient one.} 
        \experienceItemListEnd
       \vspace{4.5pt}
        \experienceDeatilsWithCert
        {Fractal.ai}
        {Software Development Engineer Intern}
        {05/2024 – 07/2024}
        {React.js, JavaScript, Node.js, MySQL}
        {Remote}
        {https://drive.google.com/file/d/1ZvOXi7rF7RsdwN81TFdBPw-0deks7ZIX/view}
        \vspace{-5pt}
        \experienceItemListStart
            \ProjectItem{Architected automated test scripts using Codecept.js and Mocha.js to ensure a 100\% bug-free user experience.}
            \ProjectItem{Contributed to 2 projects utilizing React.js, Node.js and MySQL, enhancing front-end interfaces.}
            \ProjectItem{Tuned prompt engineering for 4 LLMs to achieve significant improvements in model outputs.}
        \experienceItemListEnd
       \vspace{3.5pt}
    \resumeSubHeadingListEnd